GLMM

### 2023-12-01 Code/GLMM.Rmd
making sure everything is consistent
blinded supplemental files, removed noprelim data from readme

---
title: "GLMM"
author: "Owen Fiore"
date: "2023-11-03"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

@@

### 9
This test compares the full model with the heat effect only model.
```{r}
anova(with2022_heat_gamma_log, with2022_two_effect_gamma_log)
```
This anova test determined that the two effect model is an improvement over the
heat effect model. The test statistic is 0.008305 which is significant at 
$\alpha = 0.05$.

>>>>

---
title: "GLMM"
author: "Blinded"
date: "2023-12-01"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

@@

### 9
This test compares the full model with the heat effect only model.
```{r}
anova(with2022_heat_gamma_log, with2022_two_effect_gamma_log)
```
This anova test determined that the two effect model is an improvement over the
heat effect model. The p-value is 0.008305 which is significant at 
$\alpha = 0.05$.
